SIPESCA-B: a set of real data time series benchmark for traffic prediction

### 2015-06-12 paper.tex
terminando la intro

The rest of this paper is organized as follows:

COMPLETAR...

>>>>

The rest of this paper is organized as follows:
In Section \ref{sec:timeseries}, the research project within this work has been developed is presented. This section details how the time series data has been obtained.
Section \ref{sec:medidasdeerror} proposes several standar measures of error to be used when carrying out the time series predictions, so that the obtained results are comparable with those presented by other authors.
Then, a brief state of the art on methods for predicting time series is presented (Section \ref{sec:ForecastTools}).
In Section \ref{sec:Experiments}, a series of experimental results is presented on several time series, using several prediction methods and the proposed measures of error.
Finally, Section \ref{sec:Conclusions} presents a brief conclusions, followed by future works.
